---
title: "Fitness_CART"
author: "Vikas Venkat Sigatapu"
date: "10/20/2020"
output: html_document
---

##Introductionn
In this mini project, the aim is to analyze the data in the training set and classify it into A,B,C,D or E. The data contains a lot of fitness variables based on fitbit type devices and the goal is to classify them into catergories of exercise.

###Installing the packages and Librariess
caret and ggplot2 are the various packages that are required to install for importing the required libraries.

```{r}
#install.packages("caret")
#install.packages("ggplot2")
#install.packages("rpart")
#install.packages("randomForest")
```
#Importingg Librariess
caret libraryy i.e the classification and regressionn Trees are imported.
readr libraryy is used for readingg csv files in R.
```{r}
library(caret)
library(readr)
library(rpart)
library(randomForest)
```

## Gettingg the Dataa

```{r}
#Getting the Data
###reading the training dataset
trainingg <- read_csv("D:/R/Practical Machine Learning/pml-training.csv")
summary(trainingg)
#reading the test dataset
testingg <- read_csv("D:/R/Practical Machine Learning/pml-testing.csv")
summary(testingg)
```

##Exploratoryy Data Analysiss

```{r}
#Exploratory Data Analysiss
###For obtaining the type of each columnn
str(trainingg)

###For checking the number of rows and columns in the datasett, the train datasett contains 19622 rows and 160 columns.
dim(trainingg)

###Taking count for the final results
table(trainingg$classe)

```
#Cleaningg the Dataa
Dealing with missing values


```{r}
#Exploratory Data Analysis
###for obtaining the type of each columnn

Count_na = sapply(1:dim(trainingg)[2],function(x)sum(is.na(trainingg[,x])))
List_na = which(Count_na>0)
colnames(trainingg[,c(1:7)])

```
###removingg the null valuess from the trainingg sett

```{r}
trainingg = trainingg[,-List_na]
trainingg = trainingg[,-c(1:7)]
trainingg$classe = factor(trainingg$classe)
###removing the null values from the test sett
testingg = testingg[,-List_na]
testingg = testingg[,-c(1:7)]
```
#Buildingg the Modell
Decision Tree
```{r}
#Exploratory Data Analysis
###for obtaining the type of each column

Classifier = rpart(formula = classe~.,data=trainingg)
y_pred = predict(Classifier,testingg)
print(y_pred)

y_pred_actual = predict(Classifier,testingg,type="class")
print(y_pred_actual)
```

#Randomm Forestt

```{r}
#Exploratory Data Analysiss
###for obtaining the type of each columnn

rfclassifier = randomForest(formula = classe~.,data=trainingg, ntree = 10)
y_pred_rf = predict(rfclassifier,testingg)
print(y_pred_rf)
```



